\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array}
\usepackage{wrapfig}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath, amssymb, amsthm}
\usepackage{bbm}
\usepackage{wrapfig}
\usepackage{lipsum}
%\usepackage{biblatex}
\usepackage{mathtools}
\usepackage{float}
\usepackage{thmtools} % advanced theorem styles
\usepackage{enumitem} % environments for enumeration
\usepackage{tikz}
\usetikzlibrary{calc, arrows.meta}

\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric,
    doi=false,
    isbn=false,
    url=false,
    maxnames=50]{biblatex}
\addbibresource{literature.bib}


% algorithm environment
\usepackage[ruled, algosection]{algorithm2e}

%\addbibresource{references.bib}

\declaretheoremstyle[
  spaceabove=\parsep,
  spacebelow=0,
  headfont=\bfseries,
  notefont=\bfseries,
  notebraces={(}{)},
  bodyfont=\normalfont,
  postheadspace=.5em
]{definition}

\newtheoremstyle{plain}         % name
    {\parsep}                   % Space above
    {}                          % Space below
    {\itshape}                  % Body font
    {}                          % Indent amount
    {\bfseries}                 % Theorem head font
    {.}                         % Punctuation after theorem head
    {.5em}                      % Space after theorem head
    {\thmname{#1}\thmnumber{ #2}\thmnote{ \bfseries (#3)}}                 % Theorem head spec (can be left empty, meaning ‘normal’)

\declaretheorem[sharenumber=algocf]{theorem}
\declaretheorem[sharenumber=algocf]{lemma}
\declaretheorem[sharenumber=algocf]{corollary}
\declaretheorem[sharenumber=algocf]{proposition}

\declaretheorem[sharenumber=algocf]{definition}
\declaretheorem[sharenumber=algocf]{example}
\declaretheorem[sharenumber=algocf]{remark}
\declaretheorem[sharenumber=algocf]{notation}


% \newtheorem{assumption}{Assumption}
% \newtheorem{lemma}{Lemma}
% \newtheorem{proposition}{Proposition}
% \newtheorem{example}{Example}
% \newtheorem{theorem}{Theorem}
% \newtheorem{corollary}{Corollary}
% \newtheorem{remark}{Remark}
% \newtheorem{definition}{Definition}[section]


\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}

\renewcommand{\phi}{\varphi}
\renewcommand{\epsilon}{\varepsilon}

\newcommand{\stab}{\mathrm{Stab}}
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\vol}{\mathrm{vol}}
% \newcommand{\min}{\text{min}}
% \newcommand{\max}{\text{max}}
% \newcommand{\ker}{\text{ker}}
\newcommand{\im}{{\mathrm{im}}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Aut}{{\mathrm{Aut}}}

\newcommand{\T}{\mathcal{T}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\L}{\mathcal{L}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{GMI 2026}
% \author{Lukas Schnelle}

\begin{document}

\begin{abstract}
	This is joint work with Alice C. Niemeyer and Kai-Uwe Schr\"oder.\\
	A topological interlocking assembly (TIA) consists of multiple blocks which are in contact with each other, there exists a subset of the blocks that if it is fixed in place, all other blocks are also fixed in place. Geometries admitting such a TIA are known since 1735, however until recently the number of them was very low. Recent mathematical advances presented a new method of constructing large numbers of candidate geometries which in all investigated cases admitted a TIA. This method is based on the interpolation of deformed fundamental domains of crystallographic groups.
	
	This talk will present the new method as well as a generalisation to the three dimensional case. Additionally, we present results about the mechanical performance of these newly generated TIAs and new approaches to more efficiently evaluate them. Further, we present applications of TIAs from multiple interdisciplinary collaborations, including aerospace, medical devices and biology connected to civil engineering. 
	
	As this is ongoing work it might contain preliminary results and present current research hypotheses.
\end{abstract}

\newpage
% \nocite{*}
\section*{Literature}
\printbibliography[heading=bibintoc,title={Bibliography}]

\end{document}
